refnx - Neutron and X-ray reflectometry analysis in Python

### 2018-07-17 paper/manuscript.tex
PAPER: address couple of comments

\begin{abstract}
The \refnx package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. Structure construction is modular, being composed from a series of Components that each describe a subset of the interface. These Components (such as LipidLeaflet, or Spline) allow the user to parameterise their model in terms of physically relevant parameters. The Model and data are used to create an Objective, which is used to calculate residuals, log-likelihood, and log-prior probabilities of the system. Objectives are combined to perform co-refinement of multiple datasets, and mixed-area models. All parameters in the system can have a variety of Bounds applied; these bounds consist of probability distributions which represent their prior probability. The prior probability encodes a user's knowledge about the Parameter values, which allows the curve-fitting engine to direct solutions toward a more probable parameter space. Extra prior probability terms can be defined for Components, over and above those available from the Parameters alone.
Algebraic Parameter constraints are available.
The powerful curve-fitting engine offers the choice of using a normal least-squares fitting approach (with a variety of global and gradient-based optimizers) or a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters. The Bayesian approach is useful in examining parameter covariances, model selection, and variability in the resulting scattering length density profiles.

@@

The \Objective statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system. \refnx uses the \emph{scipy} package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emph{emcee} package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters. Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation. Visualisation of the samples produced by MCMC sampling is done using the \emph{corner} package \cite{corner} for scatter plot matrices. On the conclusion of a fit/sampling run each \Parameter is updated and given a standard error. For the sampling these represent the median and half the [15.87, 84.13] percentile range respectively; the latter approximates the standard deviation for a normally distributed statistic.

>>>>

\begin{abstract}
The \refnx package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. It is cross platform, and has been tested on Linux, macOS, and Windows.
Structure construction is modular, being composed from a series of Components that each describe a subset of the interface. These Components (such as LipidLeaflet, or Spline) allow the user to parameterise their model in terms of physically relevant parameters. The Model and data are used to create an Objective, which is used to calculate residuals, log-likelihood, and log-prior probabilities of the system. Objectives are combined to perform co-refinement of multiple datasets, and mixed-area models. All parameters in the system can have a variety of Bounds applied; these bounds consist of probability distributions which represent their prior probability. The prior probability encodes a user's knowledge about the Parameter values, which allows the curve-fitting engine to direct solutions toward a more probable parameter space. Extra prior probability terms can be defined for Components, over and above those available from the Parameters alone.
Algebraic Parameter constraints are available.
The powerful curve-fitting engine offers the choice of using a normal least-squares fitting approach (with a variety of global and gradient-based optimizers) or a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters. The Bayesian approach is useful in examining parameter covariances, model selection, and variability in the resulting scattering length density profiles.

@@

The \Objective statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system. \refnx uses the \emph{scipy} package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emph{emcee} package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters. The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}. However, other types of measurement errors (e.g. Poissonian) could be implemented by a subclass of \Objective and overriding the log-likelihood method.
Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation. Visualisation of the samples produced by MCMC sampling is done using the \emph{corner} package \cite{corner} for scatter plot matrices. On the conclusion of a fit/sampling run each \Parameter is updated and given a standard error. For the sampling these represent the median and half the [15.87, 84.13] percentile range respectively; the latter approximates the standard deviation for a normally distributed statistic.
